Using VariantSpark to learn population structure from genomic profiles

### 2015-10-26 doc/publications/Recomb15/recomb15.tex
Remove duplicate para and add stuff

The mean error for our \kMeans clustering models is approximately XXX. This is similar to the deep-learning approach
where they achieved an accuracy of 99\% (two misclassified individuals). Our supervised logistic regression approach,
however, improves upon this result.  With this approach, we achieve an accuracy of 100\%. This is the average across
five folds, with a standard error of 0. This is on the above three populations, ASW, CHB and GBR, that belong to the
super-populations, AFR, EAS and EUR, respectively.  As we mention in the introduction, we observed a perfect clustering
result when we cluster the entirety of these three super-populations, with an ARI of 1.0. However, when we introduce the
fourth super-population into the mix, AMR, the ARI drops to 0.84.

@@

Although memory requirements scale linearly with

>>>>

The mean error for our \kMeans clustering models is approximately XXX. This is similar to the deep-learning approach
where they achieved an accuracy of 99\% (two misclassified individuals). Our supervised logistic regression approach,
however, improves upon this result.  With this approach, we achieve an accuracy of 100\%. This is the average across
five folds, with a standard error of 0. This is on the above three populations, ASW, CHB and GBR, that belong to the
super-populations, AFR, EAS and EUR, respectively.

@@

Time and resources vary greatly between the three algorithms, with the most resource intensive being random forests.
This is likely due to RF being an ensemble method. Where logistic regression and \kMeans{} clustering build a single model,
RF is building a forest of trees. So not only is training longer, but then each sample in the test fold must be classified by each and every tree.

LR is
